---
title: "codecheck: Introduction to the codecheck package"
author: "Stephen J Eglen and Daniel Nüst"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{codecheck: Introduction to the codecheck package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Installing the package

The latest version of the package can be installed using:
```{r install, eval=FALSE}
remotes::install_github("codecheckers/codecheck")

```

## Clone the project

Clone the project that you wish to check into codecheckers/
organisation.

## Get a certificate number 

Go onto the register repo and add an issue for the new paper to
reproduce, and add an extra row at the bottom of register.csv.
Certificate numbers are simply YYYY-NNN where YYYY is the date and NNN
is a 3 digit number that starts at 001 and increases by 1 each time.

## Write a codecheck certificate

In the top-level of the repo to replicate ("the root"), start R and
run the following to generate several template files.  These will then
need to be committed into the repo.

```{r, eval=FALSE}
create_codecheck_files()
```

These create several files that need to be edited for the codecheck
process:

1. *codecheck.yml* contains the metadata for the reproduction.
2. *codecheck/codecheck.Rmd* is a suggested Rmarkdown script to
	edit, along with *Makefile* and *codecheck-preamble.sty* to help
	compile the PDF.
3. *codecheck/zenodo-codecheck.R* for help in loading the certificate
   to Zenodo along with the corresponding metadata.



## Submitting the certificate to Zenodo

There is no requirement to use the following code to generate the
record on Zenodo -- if you prefer to do it manually, that is fine.
However, we encourage codecheckers to use this API as it will save
time and ensure that certificates have similar structure.

You will first need a zenodo account and to generate a token to use
the API.  This token can be generated from
<https://zenodo.org/account/settings/applications/tokens/new/>. The
token should not be stored in your R script, but should be typed in or
read from a local file and stored in the variable `my_token` in the
file `codecheck/codecheck-zenodo.R`.

The metadata contained in `codecheck.yml` is uploaded using some
helper functions from the codecheck package.  To start with, you can
create a new empty record on Zenodo using `get_zenodo_record()` and
then store the resulting URL in `codecheck.yml`.  The rest of the
metadata can remain as before.

Once you are ready, upload the certificate itself using the
function `set_zenodo_certificate()`.  Whilst the zenodo record is in
draft form, you can delete files from the website, and then re-add
them using the API.

Once you have uploaded the certificate and checked the metadata, you
can then publish the record.





## Archive your repo onto zenodo
