---
title: "Introduction to the codecheck package"
author: "Stephen J Eglen and Daniel Nüst"
date: "`r Sys.Date()`"
output: rmarkdown::pdf_vignette
vignette: >
  %\VignetteIndexEntry{codecheck: Introduction to the codecheck package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Installing the package

The latest version of the package can be installed using:
```{r install, eval=FALSE}
remotes::install_github("codecheckers/codecheck")

```

## Clone the project

Clone the project that you wish to check into codecheckers/
organisation.

## Get a certificate number 

Go onto the register repo and add an issue for the new paper to
reproduce, and add an extra row at the bottom of register.csv.
Certificate numbers are simply YYYY-NNN where YYYY is the date and NNN
is a 3 digit number that starts at 001 and increases by 1 each time.

## Write a codecheck certificate

In the top-level of the repo to replicate ("the root"), start R and
run the following to generate several template files.  These will then
need to be committed into the repo.

```{r, eval=FALSE}
create_codecheck_files()
```

These create several files that need to be edited for the codecheck
process:

1. *codecheck.yml* contains the metadata for the reproduction.
2. *codecheck/codecheck.Rmd* is a suggested Rmarkdown script to
	edit, along with *Makefile* and *codecheck-preamble.sty* to help
	compile the PDF.
3. *codecheck/zenodo-codecheck.R* for help in loading the certificate
   to Zenodo along with the corresponding metadata.



## Submitting the certificate to Zenodo

