---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache = FALSE)

root <- find_root("codecheck.yml")
```

```{r check_sibling_template, eval=TRUE, include=FALSE}
## Warn if codecheck.qmd is also present next to this file - having both
## makes it unclear which one is the canonical certificate source.
if (file.exists(file.path(root, "codecheck", "codecheck.qmd"))) {
  warning("Both codecheck.Rmd and codecheck.qmd are present in codecheck/ - ",
          "remove one so the certificate source is unambiguous.")
}
```

```{r validate_yaml_syntax, eval=TRUE, include=FALSE}
## Validate YAML syntax - will stop rendering if YAML is invalid
codecheck::validate_yaml_syntax(file.path(root, "codecheck.yml"))
```

```{r check_certificate_id, eval=TRUE, include=FALSE}
## Check if certificate identifier is set properly and try to update from GitHub
## This will check if the certificate is a placeholder and attempt to retrieve
## the actual certificate ID from GitHub issues matching the author names

# Check if certificate is a placeholder
yml_path <- file.path(root, "codecheck.yml")
if (codecheck::is_placeholder_certificate(yml_path)) {
  message("CERTIFICATE ID NOT SET")

  # Try to automatically retrieve and update certificate from GitHub
  result <- codecheck::update_certificate_from_github(
    yml_file = yml_path,
    issue_state = "open",
    apply_update = FALSE  # Set to TRUE to automatically update
  )

  if (!is.null(result$certificate) && result$certificate != "") {
    message("\n✓ Certificate found! To apply the update, run:")
    message("\n  codecheck::update_certificate_from_github(apply_update = TRUE)")
    message("\nOr manually update codecheck.yml with certificate: ", result$certificate)
  } else {
    message("\nℹ No matching certificate found in GitHub issues.")
    message("You may need to manually set the certificate identifier in codecheck.yml")
  }
}
```

```{r codecheck_logo, echo=FALSE,results='asis'}
codecheck::latex_codecheck_logo()
```

```{r validate_certificate, echo=FALSE, results='asis'}
## Validate certificate and display warning if placeholder, or if the
## report DOI is a Zenodo concept DOI instead of a version-specific DOI
## Set strict = TRUE to fail rendering if certificate is a placeholder
## Set display_warning = FALSE to suppress the warning box in PDF output
codecheck::validate_certificate_for_rendering(
  yml_file = file.path(root, "codecheck.yml"),
  strict = FALSE,           # Set to TRUE to fail rendering
  display_warning = TRUE    # Set to FALSE to hide warning in PDF
)
```

```{r manifest, eval=TRUE, include=FALSE}
metadata <- codecheck::codecheck_metadata(root)
manifest <- metadata$manifest

dest_dir <- file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if (!dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df <- codecheck::copy_manifest_files(root, metadata,
                                             dest_dir, keep_full_path = FALSE,
                                             overwrite = FALSE
                                             )
# manifest_df <- codecheck::list_manifest_files(root, metadata, dest_dir)
```

```{r validate_metadata, eval=TRUE, include=FALSE}
## Validate metadata against OpenAlex and ORCID metadata - will fail rendering on mismatch
## Set strict = FALSE or remove this chunk if you want to skip validation
##
## ORCID name checks first try the authenticated ORCID API, then automatically
## fall back to the public, unauthenticated ORCID API for records whose name
## is publicly visible - so most checks work without any ORCID setup at all.
## skip_on_auth_error only matters if BOTH lookups fail for a record (e.g. no
## network access, or the record's name is not public); it is enabled below
## so a fresh workspace always renders even in that case.
validation_result <- codecheck::validate_contents_references(
  yml_file = file.path(root, "codecheck.yml"),
  strict = TRUE
  , skip_on_auth_error = TRUE
)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
codecheck::latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
codecheck::latex_summary_of_manifest(metadata, manifest_df, root)
```

\clearpage

# CODECHECKER notes

```{r git_sha, echo=FALSE}
gitInfo <- codecheck::get_git_info(root)
```

The GitHub repo ...
`r gitInfo`
Code was written in ...
I went through the following steps ...
One hard problem was ...
I added the following files ... using tools/methods ...

This took ... minutes to complete on {a large workstation, my laptop}.

## Recommendations

I suggest to the authors to consider the following suggestions for their next publication or workflow:

- ...

(document here if any of the suggestions were taken up by the authors in the meantime - do not remove any, keep track of contributions via feedback)

\clearpage

# Manifest files

```{r manifest_files, echo=FALSE, results="asis", width=100}
codecheck::render_manifest_files(manifest_df)
```

```{r figure_comparisons, eval=FALSE, include=FALSE, results="asis"}
## Optional: show published and reproduced figures together. Create the comparison
## images once from the R console in this directory; check that the license of the
## article allows reusing its figures, and pair the figures explicitly, because the
## order of images in a PDF may differ from the page layout:
##   figures <- codecheck::extract_pdf_figures("article.pdf", "published", pages = 5:9)
##   codecheck::compare_figures(figures$file[c(1, 2)], c("outputs/fig1.png", "outputs/fig2.png"),
##     labels = c("Published (Author et al., YYYY, CC BY 4.0)", "Reproduced (CODECHECK)"))
## Then set eval=TRUE and include=TRUE, and add a heading such as
## "# Comparison of figures" above this chunk.
codecheck::render_figure_comparisons(c("comparison/comparison-1.jpg", "comparison/comparison-2.jpg"),
  captions = paste("Figure", 1:2, "of the article: published (top) and reproduced (bottom)."))
```

\clearpage

## Acknowledgements

I would like to thank ... for ... [promptly answering any
queries/providing updates; assitance with X; ...].

# Citing this document

```{r, results='asis',echo=FALSE}
codecheck::cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# handle Zenodo publication (alternative to codecheck-zenodo.R !)
library("zen4R")
zenodo <- ZenodoManager$new(token = zenodoToken) # assumes Zenodo token is configured via .Renviron
record <- codecheck::get_or_create_zenodo_record(zenodo, codecheck::codecheck_metadata(root))
record <- codecheck::upload_zenodo_metadata(zenodo, record, codecheck::codecheck_metadata(root))
codecheck::upload_zenodo_certificate(zenodo = zenodo, record = record$id, certificate = file.path(root, "codecheck", "codecheck.pdf"))
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document")
```
