---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache = FALSE)

root <- find_root("codecheck.yml")
```

```{r validate_yaml_syntax, eval=TRUE, include=FALSE}
## Validate YAML syntax - will stop rendering if YAML is invalid
validate_yaml_syntax(file.path(root, "codecheck.yml"))
```

```{r check_certificate_id, eval=TRUE, include=FALSE}
## Check if certificate identifier is set properly and try to update from GitHub
## This will check if the certificate is a placeholder and attempt to retrieve
## the actual certificate ID from GitHub issues matching the author names

# Check if certificate is a placeholder
yml_path <- file.path(root, "codecheck.yml")
if (is_placeholder_certificate(yml_path)) {
  message("CERTIFICATE ID NOT SET")

  # Try to automatically retrieve and update certificate from GitHub
  result <- update_certificate_from_github(
    yml_file = yml_path,
    issue_state = "open",
    apply_update = FALSE  # Set to TRUE to automatically update
  )

  if (!is.null(result$certificate) && result$certificate != "") {
    message("\n✓ Certificate found! To apply the update, run:")
    message("\n  update_certificate_from_github(apply_update = TRUE)")
    message("\nOr manually update codecheck.yml with certificate: ", result$certificate)
  } else {
    message("\nℹ No matching certificate found in GitHub issues.")
    message("You may need to manually set the certificate identifier in codecheck.yml")
  }
}
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r validate_certificate, echo=FALSE, results='asis'}
## Validate certificate and display warning if placeholder
## Set strict = TRUE to fail rendering if certificate is a placeholder
## Set display_warning = FALSE to suppress the warning box in PDF output
validate_certificate_for_rendering(
  yml_file = file.path(root, "codecheck.yml"),
  strict = FALSE,           # Set to TRUE to fail rendering
  display_warning = TRUE    # Set to FALSE to hide warning in PDF
)
```

```{r manifest, eval=TRUE, include=FALSE}
metadata <- codecheck_metadata(root)
manifest <- metadata$manifest

dest_dir <- file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if (!dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df <- copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE
                                  )
# manifest_df <- list_manifest_files(root, metadata, dest_dir)
```

```{r validate_crossref, eval=TRUE, include=FALSE}
## Validate metadata against CrossRef and ORCID metadata - will fail rendering on mismatch
## Set strict = FALSE or remove this chunk if you want to skip validation
validation_result <- validate_contents_references(
  yml_file = file.path(root, "codecheck.yml"),
  strict = TRUE
)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

This code was (not) straightforward to codecheck.
[... ADD MORE INTERESTING FINDINGS HERE..]

\clearpage

# CODECHECKER notes

```{r git_sha, echo=FALSE}
gitInfo <- ""
if(git2r::in_repository(root)) {
  gitInfo <- paste0("This check is based on the commit `", git2r::last_commit()$sha, "`.")
}
```

The GitHub repo ...
`r gitInfo`
Code was written in ...
I went through the following steps ...
One hard problem was ...
I added the following files ... using tools/methods ...

This took ... minutes to complete on {a large workstation, my laptop}.

## Recommendations

I suggest to the authors to consider the following suggestions for their next publication or workflow:

- ...

(document here if any of the suggestions were taken up by the authors in the meantime - do not remove any, keep track of contributions via feedback)

\clearpage

# Manifest files

```{r, echo=FALSE, results="asis", width=100}
for (i in c(1:nrow(manifest_df))) {
  path <- manifest_df[i, "dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    # include graphics with knitr has to happen at top level in chunks, see https://github.com/yihui/knitr/issues/1260
    # see also https://stackoverflow.com/questions/51268623/insert-images-using-knitrinclude-graphics-in-a-for-loop
    # knitr::include_graphics(manifest_df[1, "dest"], error = TRUE)
    # Therefore, generate Markdown code here:
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", manifest_df[i,"comment"], "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "(xls|xlsx)")) {
    cat("## ", basename(path), "\n\n", "Partial content of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(readxl::read_excel(path))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "(htm|html)")) {
    if(Sys.which("wkhtmltopdf") != "") {
      cat("## ", basename(path), "\n\n", "Content of HTML file (starts on next page):", "\n\n")
      out_file <- paste0(path, ".pdf")
      system2("wkhtmltopdf", c(shQuote(path), shQuote(out_file)))
      cat(paste0("\\includepdf[pages={-}]{", out_file, "}"))
      cat("\n\n End of ", basename(path), "on previous page.", "\n\n")
    } else {
      cat("## ", basename(path), "\n\n")
      cat("Cannot inlcude output file as figure.")
    }
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

\clearpage

## Acknowledgements

I would like to thank Dr Bhatt and his team for promptly answering any
queries I had with this reproduction.  CODECHECK is financially
supported by the Mozilla foundation.

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```


```{r, include=FALSE, eval=FALSE}
# handle Zenodo publication (alternative to codecheck-zenodo.R !)
library("zen4R")
zenodo <- ZenodoManager$new(token = zenodoToken) # assumes Zenodo token is configured via .Renviron
record <- codecheck::get_or_create_zenodo_record(zenodo, codecheck_metadata(root))
record <- codecheck::upload_zenodo_metadata(zenodo, record, codecheck_metadata(root))
codecheck::upload_zenodo_certificate(zen = zenodo, record = record$id, certificate = file.path(root, "codecheck", "codecheck.pdf"))
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document")
```
